%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Conference presentations}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cvpresen
{Faraday Joint Interest Group Conference } % Event
{\textbf{Poster:} \normalfont``Calculating High Precision Two-Electron Correlation Data''} % Role
{Virtual} % Location
{March. 2021} % Date(s)
{}

\cvpresen
{Life Sciences Research Symposium} % Event
{\textbf{Talk:} \normalfont``The Quantum Mechanical three-body problem: Where Physics meets Chemistry''} % Role
{University of Sussex, UK} % Location
{January. 2021} % Date(s)
{}

\cvpresen
{STEM for Britain 2020} % Event
{\textbf{Poster:} \normalfont``Electron Correlation in the Real World''} % Role
{Houses of Parliament, UK} % Location
{March. 2020} % Date(s)
{}

\cvpresen
{\Rmnum{10} Congress of the International Society for Theoretical Chemical Physics} % Event
{\textbf{Poster:} \normalfont``Calculating High Precision Two-Electron Correlation Data''} % Role
{Tromso, Norway} % Location
{July. 2019} % Date(s)
{}

\cvpresen
{School of Physical Sciences Quantum Theory and Simulation Seminar Series} % Event
{\textbf{Talk:} \normalfont``The Quantum Mechanical three-body problem: Where Physics meets Chemistry''} % Role
{University of Kent, UK} % Location
{April. 2019} % Date(s)
{}

\cvpresen
{Young Modellers forum} % Event
{\textbf{Talk:} \normalfont``Going beyond standard approximations in quantum chemistry''} % Role
{University of Greenwich, UK} % Location
{Nov. 2017} % Date(s)
{}

%------------------------------------------------

\cvpresen
{Quantum Physics and Quantum Technology} % Event
{\textbf{Talk:} \normalfont``Excited S states of two electron atoms''} % Role
{Berlin, Germany} % Location
{Sept. 2017} % Date(s)
{ % Description(s)
}

%------------------------------------------------

\cvpresen
{School of Life Sciences Research Symposium} % Event
{\textbf{Poster:} \normalfont``Quantum effects of particle motion in atomic and molecular three-particle systems''} % Role
{University of Sussex, UK} % Location
{Sept. 2016} % Date(s)
{ % Description(s)
}

%------------------------------------------------

\cvpresen
{\Rmnum{9} Congress of the International Society for Theoretical Chemical Physics} % Event
{\textbf{Poster:} \normalfont``Quantum effects of particle motion in atomic and molecular three-particle systems''} % Role
{North Dakota, USA} % Location
{July. 2016} % Date(s)
{ % Description(s)
}

%------------------------------------------------

\cvpresen
{IMAMPC conference} % Event
{\textbf{Poster:} \normalfont``Intracule and centre of mass particle densities for atomic and molecular three-particle systems''} % Role
{Birmingham, UK} % Location
{August. 2015} % Date(s)
{ % Description(s)
}

%------------------------------------------------

\cvpresen
{IMAMPC conference} % Event
{\textbf{Session Chair:} \normalfont``General theory session''} % Role
{Birmingham, UK} % Location
{August. 2015} % Date(s)
{ % Description(s)
}

%------------------------------------------------

\cvpresen
{Gyorffy-SuperMagCorrelation meeting} % Event
{\textbf{Poster:} \normalfont``Magnetic monopoles in spin ice''} % Role
{Bristol, UK} % Location
{Sept. 2014} % Date(s)
{ % Description(s)
}

%------------------------------------------------

\cvpresen
{Physical sciences research symposium} % Event
{\textbf{Talk:} \normalfont``Magnetic monopoles in spin ice''} % Role
{University of Kent, UK} % Location
{May. 2014} % Date(s)
{ % Description(s)
}

%------------------------------------------------

\end{cventries}