%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Teaching}

%----------------------------------------------------------------------------------------
%	Teaching
%----------------------------------------------------------------------------------------

%------------------------------------------------

\begin{cvhonors}

%------------------------------------------------

\cvhonor
{Programming for Chemists} % Award
{\textit{School of Life Sciences, University of Sussex}.\newline I independently created and taught a scientific programming course using Jupyter for staff and students at Sussex. It involved seven workshops to introduce beginners to the Python language, covering: basic notation, data types, control flow, NumPy, file input/output, physical chemistry and the basics of machine learning applied to the physical sciences. Emphasis was placed on how programming applies to solving scientific problems.} % Event
{} % Location
{2019-2020} % Date(s)

%------------------------------------------------

\cvhonor
{Computer Lab Manager and Research Supervisor} % Award
{\textit{School of Life Sciences, University of Sussex}. \newline I am the current computer lab manager in the research group responsible for maintaining all computer resources alongside resolving computer and programming related issues. I also provide day to day supervision of PhD and MChem project students in the Cox group in their research and personal development.} % Event
{} % Location
{2015-Present} % Date(s)

%------------------------------------------------

\cvhonor
{Lecturer and Associate Tutor} % Award
{\textit{School of Life Sciences, The University of Sussex, UK}. \newline Within my current role I deliver lectures on mathematics and data analysis for first year students. I have also assisted in teaching mathematics, data analysis, point group symmetry, bonding and spectroscopy, and computational chemistry across multiple year groups from foundation to final year students in the bioscience and chemistry departments. This involved problem based workshops and marking.} % Event
{} % Location
{2014-Present} % Date(s)

%------------------------------------------------

\cvhonor
{Student Mentor} % Award
{\textit{School of Physical Sciences, University of Kent, UK}. \newline In my final year of my master's degree I was a student mentor and assisted students in the lower years in several modules including relativity, optics and Maxwells' equations, cosmology and advanced mathematical physics. This involved revision of the content covered in lectures and advising with problem sets.} % Event
{} % Location
{2013-2014} % Date(s)

%------------------------------------------------

\end{cvhonors}

