%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Transferable skills training}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cvtransfer
{Hariri Institute for Computing} 
{Advancing Chemical and Materials Science through Machine Learning} % Event
{June. 2021} % Date(s)
{}
{Machine learning symposium highlighting recent advances and applications of machine learning to the chemical and physical sciences.
}

%------------------------------------------------

\cvtransfer
{IT Center for Science (CSC)} 
{Quantum Computing and Programming Workshop} % Event
{May. 2021} % Date(s)
{}
{Participant in a quantum computing workshop where details of quantum computing were given along with completing various hands on examples of programming quantum algorithms on a Quantum Processing Unit (QPU).
}

%------------------------------------------------

\cvtransfer
{Elsevier} 
{Certified Peer Reviewer Course} % Event
{July. 2020} % Date(s)
{}
{Online peer review course organised by Elsevier which offered a thorough grounding in the principles and practice of refereeing publications.
}

%------------------------------------------------

\cvtransfer
{Institute of Physics (IOP)} 
{MapleSoft training course} % Event
{March. 2016} % Date(s)
{}
{Training course sponsored by MapleSoft entitled ``\textit{Applying the power of computer algebra to theoretical physics''}, which covered various applications of Maple in theoretical calculations and showcased new software features.
}

%------------------------------------------------

\cventry
{Royal Society of Chemistry}
{Virtual winter school for computational chemistry} % Event
{Feb. 2016} % Date(s)
{}
{This online conference hosted talks along with interactive question and answer sessions, on a variety of subjects from computational solid state physics and chemistry, to molecular excited state calculations and inclusion of relativistic corrections.
}

%------------------------------------------------

%\cvtransfer
%{University of Sussex} 
%{Presentation Delivery} % Event
%{Jan. 2016} % Date(s)
%{University of Sussex}
%{Training course to develop public speaking skills and improve delivery of scientific research theory and outcomes.
%}

%------------------------------------------------

%\cventry
%{Royal Society of Chemistry} % Role
%{NSCCS workshop} % Event
%{Sept. 2014} % Date(s)
%{Imperial college London}
%{Workshop organised by the EPSRC UK National Service for Computational Chemistry Software (NSCCS) to learn and use the Gaussian09 software package.
%}

%------------------------------------------------

\end{cventries}

